Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-11-07 Robustness-Methods-and-Results.Rmd
headers fixed
open science practices linked

The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A. Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.

@@

\subsection{Study 1}

@@

\subsubsection{Results}

@@

\subsection{Study 2}

@@

\subsection{Study 3}

>>>>

As with the main analyses, full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A. Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.

@@

\subsection{Results}

\subsubsection{Study 1}

@@

@@

\subsubsection{Study 2}

@@

\subsubsection{Study 3}
